Image Forensics using Reflections on Curved Surfaces

### 2014-02-26 paper/main.tex
final revisions

\chapter{Mathematical Techniques}
\section{Approach}
The goal of this analysis is to find a method for determining reflection consistency that is general enough to not need to know the camera parameters, in the same vein as the existing techniques for planar mirrors. To simplify the geometry of this analysis, we will restrict the form of our non-planar mirrors to be spherical. Quadric surfaces in general are likely to be good enough for typical use cases because most general curves encountered in the real world can be approximated as either a quadric surface or a set of quadric surfaces.

@@

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{normal-reflection}
	\caption{Given a camera location $C$, a point $P$ on an object and its corresponding reflection $R$, the ray $PR$ appears equivalent to the ray $PB$ from the point of view of the camera. The ray $PR$ is also perpendicular to the surface normal $N$. Since all of the points in this diagram must be coplanar, this holds true in 3D space. \cite[Fig.~2]{obrien12}}
	\label{normal-reflection}
\end{figure}

@@

\section{Reflective Sphere Geometry}
\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{colinear-radius}
	\caption{Since the point $P$, the reflection point $B$, the camera $C$, and the normal $N$ are all coplanar, and $N$ is an extension of the radius of a sphere, then $PB$ and any radius on this cross-section of the sphere must be coplanar.}
	\label{colinear-radius}
\end{figure}

@@

Finally, in order to be able to analyze most curved surfaces, methods will need to be developed to analyze reflections on other quadric surfaces, such as cylinders and cones. In these cases it would probably be necessary to develop a reliable method for estimating the normal, as these shapes are not regular as viewed from any angle like a sphere.

>>>>

\chapter{Mathematical Techniques}
\section{Approach}
The goal of this analysis is to find a method for determining reflection consistency that is general enough to not require knowledge of the camera parameters, in the same vein as the existing techniques for planar mirrors. To simplify the geometry of this analysis, we will restrict the form of our non-planar mirrors to be spherical. Quadric surfaces in general are likely to be good enough for typical use cases because most general curves encountered in the real world can be approximated as either a quadric surface or a set of quadric surfaces.

@@

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{normal-reflection}
	\caption{Given a camera location $C$, a point $P$ on an object and its corresponding reflection $R$, the ray $PR$ appears equivalent to the ray $PB$ from the point of view of the camera. The ray $PR$ is also parallel to the surface normal $\hat{N}$. Since all of the points in this diagram must be coplanar, this holds true in 3D space. \cite[Fig.~2]{obrien12}}
	\label{normal-reflection}
\end{figure}

@@

\section{Reflective Sphere Geometry}
\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{colinear-radius}
	\caption{Since the point $P$, the reflection point $B$, the camera $C$, and the normal $\hat{N}$ are all coplanar, and $\hat{N}$ is an extension of the radius of a sphere, then $PB$ and any radius on this cross-section of the sphere must be coplanar.}
	\label{colinear-radius}
\end{figure}

@@

Finally, in order to be able to analyze most curved surfaces, methods will need to be developed to analyze reflections on other quadric surfaces, such as cylinders and cones. In these cases it would probably be necessary to develop a reliable method for estimating the normal, as these shapes are not regular as viewed from any angle as is a sphere.
